---
title: ""
aliases: [/news/]
comments: false
format:
  html:
    toc: false
execute:
  echo: false
---

```{r}
library(yaml)

`%||%` <- function(a,b) if (is.null(a) || identical(a,"")) b else a

parse_date <- function(s){
  s <- trimws(as.character(s %||% ""))
  if (grepl("^\\d{4}-\\d{2}-\\d{2}$", s)) return(as.Date(s))
  if (grepl("^\\d{4}-\\d{2}$", s))       return(as.Date(paste0(s,"-01")))
  if (grepl("^\\d{2}/\\d{4}$", s)) { p <- strsplit(s,"/",fixed=TRUE)[[1]]; return(as.Date(sprintf("%s-%s-01", p[2], p[1]))) }
  if (grepl("^\\d{4}$", s))              return(as.Date(paste0(s,"-01-01")))
  as.Date(NA)
}
fmt_date <- function(d) if (is.na(d)) "" else format(d, "%b %Y")

read_news <- function(paths = c("data/news.yaml","_data/news.yaml")){
  path <- paths[which(file.exists(paths))[1]]
  if (is.na(path)) stop("news.yaml not found in: ", paste(paths, collapse=", "))
  x <- yaml::read_yaml(path)
  items <- if (!is.null(x$news)) x$news else x

  rows <- lapply(items, function(it) {
    d <- parse_date(it$date)
    tag <- (it$category %||% it$tag) %||% NA  # prefer explicit category
    list(
      date = d, when = fmt_date(d),
      desc = it$description %||% "",
      tag  = tag,
      pin  = isTRUE(it$pin),
      h = it$hlink %||% NA, a = it$alink %||% NA,
      s = it$slink %||% NA, p = it$pdf   %||% NA, e = it$extra %||% NA
    )
  })
  # newest first; undated last
  ord <- order(vapply(rows, function(r) if (is.na(r$date)) as.Date("0001-01-01") else r$date,
                      as.Date("0001-01-01")), decreasing = TRUE)
  rows[ord]
}

# fallback tagging if some legacy items lack `category`
infer_tag <- function(desc){
  d <- tolower(desc)
  if (grepl("\\b(preprint|published|paper|journal|chapter|oup|lingbuzz|doi)\\b", d)) return("publication")
  if (grepl("\\b(hsp|lsa|plc|tu\\+|workshop|talk|poster|puzzles of agreement|usc|oxford)\\b", d)) return("talk")
  if (grepl("\\b(site|website)\\b", d)) return("site")
  if (grepl("\\b(candidacy|defend|defense|qualified|advance|visiting)\\b", d)) return("milestone")
  NA
}

tag_badge <- function(tag){
  if (is.na(tag)) return("")
  map <- list(
    talk="ðŸŽ¤ talk",
    publication="ðŸ“„ pub",
    milestone="ðŸ milestone",
    site="ðŸŒ site"
  )
  txt <- map[[tag]] %||% tag
  sprintf('<span class="news-badge">%s</span>', txt)
}

link_line <- function(r){
  L <- character()
  if (!is.na(r$h)) L <- c(L, sprintf('<a href="%s" target="_blank">handout</a>',  r$h))
  if (!is.na(r$a)) L <- c(L, sprintf('<a href="%s" target="_blank">abstract</a>', r$a))
  if (!is.na(r$s)) L <- c(L, sprintf('<a href="%s" target="_blank">slides</a>',   r$s))
  if (!is.na(r$p)) L <- c(L, sprintf('<a href="%s" target="_blank">pdf</a>',      r$p))
  if (!is.na(r$e)) L <- c(L, r$e)  # may contain HTML
  if (length(L)) sprintf('<div class="news-links">%s</div>', paste(L, collapse=' Â· ')) else ""
}

render_highlights_html <- function(rows, n = 3){
  if (n <= 0) return("")
  pinned <- vapply(rows, function(r) isTRUE(r$pin), logical(1))
  picks <- if (any(pinned)) rows[pinned] else rows
  picks <- head(picks, n)
  if (!length(picks)) return("")
  cards <- vapply(picks, function(r){
    tg <- r$tag; if (is.na(tg)) tg <- infer_tag(r$desc)
    sprintf('<article class="news-card">
      <div class="news-card-top">%s<time class="news-when">%s</time></div>
      <div class="news-desc">%s</div>%s
    </article>', tag_badge(tg), r$when, r$desc, link_line(r))
  }, character(1))
  paste0('<section class="news-highlights"><h2>Highlights</h2><div class="news-grid">',
         paste(cards, collapse = ""), '</div></section>')
}

render_feed_html <- function(rows){
  items <- vapply(rows, function(r){
    tg <- r$tag; if (is.na(tg)) tg <- infer_tag(r$desc)
    sprintf('<li class="news-item">
      <div class="news-line"><time class="news-when">%s</time>%s</div>
      <div class="news-desc">%s</div>%s
    </li>', r$when, tag_badge(tg), r$desc, link_line(r))
  }, character(1))
  paste0('<section class="news-feed"><h2>All updates</h2><ul class="news-items">',
         paste(items, collapse = ""), '</ul></section>')
}

```

```{r}
#| results: asis
rows <- read_news()
html <- paste0(
  render_highlights_html(rows, n = 2),  # set n = 0 to disable Highlights
  render_feed_html(rows)
)
knitr::asis_output(html)



```

<style>

/* ========== layout ========== */
.news-highlights {
  margin: 1.25rem 0 1rem;
}
.news-grid {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(260px, 1fr));
  gap: .85rem;
}

/* ========== highlight cards ========== */
.news-card {
  background: var(--quarto-body-bg, #fff);
  border: 1px solid var(--quarto-border-color, #e5e7eb);
  border-radius: .9rem;
  padding: .9rem 1rem;
}
.news-card-top {
  display: flex;
  align-items: center;
  justify-content: space-between;
  gap: .5rem;
  margin-bottom: .35rem;
}

/* ========== feed list ========== */
.news-feed h2 {
  margin-top: 1rem;
}
.news-items {
  list-style: none;
  padding: 0;
  margin: .5rem 0 0 0;
}
.news-item {
  padding: .7rem .25rem;
  border-bottom: 1px dashed var(--quarto-border-color, #e5e7eb);
}
.news-item:last-child {
  border-bottom: 0;
}
.news-line {
  display: flex;
  align-items: center;
  gap: .5rem;
  flex-wrap: wrap;
  margin-bottom: .15rem;
}

/* ========== atoms ========== */
.news-badge {
  font-size: .8em;
  padding: .1rem .5rem;
  border: 1px solid var(--quarto-border-color, #e5e7eb);
  border-radius: 999px;
  line-height: 1;
}
.news-when {
  font-weight: 600;
  white-space: nowrap;
  opacity: .9;
}
.news-desc {
  line-height: 1.4;
}
.news-links {
  margin-top: .2rem;
  font-size: .95em;
  white-space: nowrap;
}

/* ========== links ========== */
.news-links a {
  text-decoration: none;
  border-bottom: 1px dotted currentColor;
  transition: opacity .15s ease, border-color .15s ease;
}
.news-links a:hover,
.news-links a:focus {
  opacity: .8;
  border-bottom-color: transparent;
}

/* ========== small screens ========== */
@media (max-width: 640px) {
  .news-grid { grid-template-columns: 1fr; }
  .news-item { padding: .6rem 0; }
}

/* ========== dark-mode tweaks (optional) ========== */
@media (prefers-color-scheme: dark) {
  .news-card {
    background: rgba(255,255,255,.03);
    border-color: rgba(255,255,255,.12);
  }
  .news-item {
    border-bottom-color: rgba(255,255,255,.12);
  }
  .news-badge {
    border-color: rgba(255,255,255,.2);
  }
}


</style>